Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-17 lqg-strings.tex
Added to Einstein-Cartan string section

This is where we run into a problem. There is no way to express translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix valued group on a point living in $\mbb{R}^{d+1}$. In order to incorporate translations we have to resort to a trick and introduce an extra ``dummy'' dimension for the background manifold. Now we have $d+2$ embedding fields which we can write as:
\begin{equation}
	X^A := \{X^0, \vec X, X^r\} = \{X^\mu, X^r\},
\end{equation}
where $X^\mu = \{X^0, \vec X\}$ are the fields we had originally and $X^r$ is our new ``dummy'' co-ordinate.

treating the $X$'s as co-ordinates for the bulk background and also as

>>>>

This is where we run into a problem. There is no way to express translations in $d+1$ dimensions as the action of a $d+1$ dimensional matrix valued group on a point living in $\mbb{R}^{d+1}$. In order to incorporate translations we have to resort to a trick and introduce an extra ``dummy'' dimension for the background manifold. Now we have $d+2$ embedding fields which we can write as:
\begin{equation}
	X^A := \{X^0, \vec X, X^r\} = \{X^\mu, X^r\},
\end{equation}
where $X^\mu = \{X^0, \vec X\}$ are the fields we had originally and $X^r$ is our new ``dummy'' co-ordinate. As we will see this dimension will turn out to have a very important physical interpretation in the context of Einstein-Cartan geometry.

\subsection{Gauging Translations}\label{sec:translation_gauge}

There is a very generic way in which one can introduce translations in the form of matrix valued transformations acting on vector (or one-form) objects [ref wikipedia]. For instance if we have a vector $\vec{x} = (x,y)$, rotations are given by $2 \times 2$ matrices. Now we add a dummy $'r'$ co-ordinate to our vector and set it equal to one, so our new vector is of the form: $\vec{X} = (x,y,r=1)$. Now the matrices which act on this vector will be three dimensional. One such matrix has the form:
\begin{equation}
	\mb{R} = \begin{pmatrix}
		a & b & t_x \\
		c & d & t_y \\
		0 & 0 & 1
	\end{pmatrix}.
\end{equation}
Here the left upper diagonal $2\times 2$ block corresponds to the usual 2d rotations, while the new off-diagonal elements $(t_x, t_y)$ parametrize the amount we wish to displace our original vector $(x,y)$. Under the action of $\mb{R}$ (with the rotation component fixed to be identity), our vector becomes:
\begin{equation}\label{eqn:affine-transform}
	\mb{R} \vec X = \begin{pmatrix}
		x + t_x \\
		y + t_y \\
		1
	\end{pmatrix}.
\end{equation}
One might point out that the matrix $\mb{R}$ is not symmetric, as one would require of an orthogonal transformation. If we make $\mb{R}$ symmetric, then under the above transformation the third (projective) component of the 3-vector will no longer be equal to one.
\begin{equation}\label{eqn:affine-transform}
	\mb{R} \vec X = \begin{pmatrix}
		x + t_x \\
		y + t_y \\
		x t_x + y t_y + 1
	\end{pmatrix}.
\end{equation}
